The Anatomy of a Temporal Summarization System

### 2015-01-27 algorithm/salience.tex
Added features figure, event figure, and updated wikipedia lm figure

>>>>

\begin{figure}[t!]
\begin{tabular}{| l |} 
\hline
\textbf{Basic Features}\\
$\cdot$ Sent. position (normalized by doc. length) \\
$\cdot$ Sent. length \\
$\cdot$ Ratio of punc. to non-punc. chars. \\
$\cdot$ Ratio of caps. to non-caps. chars. \\
$\cdot$ Ratio of lowercase to other chars. \\
$\cdot$ Ratio of uppercase to other chars. \\
$\cdot$ \# of caps. words (normalized by \# of words)\\
$\cdot$ \# of Person, Location, Org. Date, Number,\\
$\;\;$ Ordinal, Percent, Money, Set, Misc  N.E. tags \\
$\;\;$ (normalized by \# of words)\\
\hline
\textbf{Query Features}\\
$\cdot$ \% of query words covered by sent.\\
$\cdot$ Total query matches.\\
$\cdot$ Total event-type synonyms/hypernyms/hyponyms\\
$\;\;$ coverage.\\
$\cdot$ Total event-type synonyms/hypernyms/hyponyms\\
$\;\;$ matches.\\
\hline
\textbf{Language Model Features}\\
$\cdot$ Avg. token log probability (domain lang. model)\\
$\cdot$ Avg. token log probability (background lang. model)\\
\hline
\textbf{Geo-tag Features}\\
$\cdot$ Median document distance to nearest location \\
$\;\;$ cluster (current hour).\\
$\cdot$ Median document distance to nearest location \\
$\;\;$ clusters (previous hour).\\
$\cdot$ Distance of first location in doc. to nearest location \\
$\;\;$ cluster (current hour).\\
$\cdot$ Distance of first location in doc. to nearest location \\
$\;\;$ cluster (previous hour).\\
\hline
\textbf{Temporal Features}\\
$\cdot$ Avg. tf-idf at current time.\\
$\cdot$ Change in avg. tf-idf since previous hour (up to\\
$\;\;$  24 hours).\\
$\cdot$ Time since query/event start.\\
\hline
\end{tabular}
\caption{Salience model features.}
\end{figure}

### 2015-01-27 methods.tex
Added features figure, event figure, and updated wikipedia lm figure

\begin{figure*}
        \begin{center}
\begin{tabular}{| p{5cm} c c |}
\hline
Event & WP Categories & No. Docs/Sents/Words\\
\hline \hline
Boston\_Marathon\_bombings \newline
Christopher\_Dorner\_shootings\_and\_manhunt \newline 
 In\_Amenas\_hostage\_crisis
& Terrorism, Mass Shootings & 33,732/1,139,588/26,201,659  \\
\hline
 Cyclone\_Oswald \newline
Early\_2012\_European\_cold\_wave \newline
February\_2013\_noreaster \newline & Weather events & 35,554/591,850/12,794,438  \\
\hline
Costa\_Concordia\_disaster & Accidents & 22,874/732,945/16,520,242 \\
\hline
Chelyabinsk\_meteor & Earthquakes & 14,515/283,509/6,135,803  \\
\hline
Port\_Said\_Stadium\_riot \newline
2012\_Afghanistan\_Quran\_burning\_protests \newline
2011-13\_Russian\_protests \newline
2012\_Romanian\_protests \newline
2012-13\_Egyptian\_protests \newline
2013\_Bulgarian\_protests\_against\_the\_Borisov\_cabinet \newline
2013\_Shahbag\_protests & Activism\_by\_type & 464,657/11,254,122/250,172,896  \\
\hline
\end{tabular}
\caption{Domain specific Wikipedia corpora for semantic similarity and 
language models. }
\end{center}
\end{figure*}

>>>>

\begin{figure*}
        \begin{center}
\begin{tabular}{| p{5cm} c c |}
\hline
Event & WP Categories & No. Docs/Sents/Words\\
\hline \hline
2012 Aurora shooting \newline
Wisconsin Sikh temple shooting\newline 
2012 Tel Aviv bus bombing \newline
Boston\_Marathon\_bombings \newline
Christopher\_Dorner\_shootings\_and\_manhunt \newline 
 In\_Amenas\_hostage\_crisis
& Terrorism, Mass Shootings & 33,732/1,139,588/26,201,659  \\
\hline
Hurricane Isaac (2012) \newline
Hurricane Sandy \newline
Typhoon Bopha \newline
2012 Guatemala earthquake \newline
 Cyclone\_Oswald \newline
Early\_2012\_European\_cold\_wave \newline
February\_2013\_noreaster \newline & Natural Disasters & 35,554/591,850/12,794,438  \\
\hline
2012 Buenos Aires Rail Disaster
2012 Pakistan garment factory fires
Costa\_Concordia\_disaster & Accidents & 22,874/732,945/16,520,242 \\
\hline
Chelyabinsk\_meteor & Astronomy & 14,515/283,509/6,135,803  \\
\hline
Port\_Said\_Stadium\_riot \newline
2012\_Afghanistan\_Quran\_burning\_protests \newline
2011-13\_Russian\_protests \newline
2012\_Romanian\_protests \newline
2012-13\_Egyptian\_protests \newline
2013\_Bulgarian\_protests\_against\_the\_Borisov\_cabinet \newline
2013\_Shahbag\_protests & Activism\_by\_type & 464,657/11,254,122/250,172,896  \\
\hline
\end{tabular}
\caption{Domain specific Wikipedia corpora for semantic similarity and 
language models. }
\end{center}
\end{figure*}
